Coherent optical association of single molecules

### 2020-08-27 paper.tex
results

We locate the Raman resonance for the atom to molecule transition at $770... MHz$ (figure \todo{}) with a $15 mW$ tweezer at $288... GHz$ which corresponds to a $... GHz$ single photon detuning.
The background level of $...\%$ corresponds to the propability of preparing the two atoms in the relative motional ground state using interaction shift spectroscopy. When the atoms are transfered into molecule by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imagine step.
\todo{more explanation of detection?}
\todo{FWHM of line??}

@@

After confirming the creating of the molecule via optical Raman transition, we proceed to verify the coherence of the process. This is done by fixing the Raman frequency on the resonance and scanned the pulse time. figure ... shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $..\%$ of initial ground state atoms are transfered into the molecular state.

\todo{Atomic lifetime}

Combining the frequency and time scan allow us to accurately fit the parameters for the Raman transition.
Raman Rabi frequency
Molecular state lifetime.
The result shows that the decoherence of the Rabi oscillation is caused by finite lifetime of the molecule in the tweezer.
We can directly measure this by \todo{pulse sequence} (figure ...)...

\todo{Lifetime}

\todo{Fitting}

\todo{Scattering}

>>>>

We locate the Raman resonance for the atom to molecule transition at $770... MHz$ (figure \todo{}) with a $15 mW$ tweezer at $288... GHz$ which corresponds to a $... GHz$ single photon detuning.
The background level of $...\%$ corresponds to the propability of preparing the two atoms in the relative motional ground state using interaction shift spectroscopy. When the atoms are transfered into molecule by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imagine step.

We observed the narrowest linewidth of $.... kHz$ for the Raman resonance at a pulse time of $... ms$, which corresponds to a linewidth-pulsetime product of $...$. This is consistent with the expected value of $...$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent. In order to verify the coherence of the transfer directly, we fixed the Raman frequency on the resonance and scanned the pulse time. figure ... shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $..\%$ of initial ground state atoms are transfered into the molecular state.

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state. We also account for atomic state loss by measuring the single and two body lifetime for the atomic state (figure ...). The result suggests that our transfer has a Raman Rabi frequency of and the molecule we form has a lifetime of $...$. We can also directly verify this result by measuring the lifetime of the molecule directly. This is done by applying a reverse Raman pulse to dissociate the molecule back to atoms after a variable wait time. The result of the direct measurement shows a molecular lifetime consistent with our fitting of the Raman transition data.

The molecule lifetime measured in the experiment is $...$ larger than the expected value of $...$ calculated from ..... By measuring the lifetime for different tweezer powers, we observed a linear dependency of the lifetime (fig ...). This confirms that the short lifetime is mainly caused by scattering from the tweezer light rather than the intrinsic lifetime of the molecule itself. Additionally, we also measured the loss rate as a function of the tweezer frequency (fig ...) which shows only a very weak dependency for a $...x$ change in the detuning from the $v=0$ excited state. This result is significantly different from the $1/\delta^2$ dependency expected from off-resonant scattering and suggests that the main source of the scattering is due to a broadband process that is not directly related to the $v=0$ excited state.

(ASE filter?)

@@
